---
title: "Weather file decomposition analysis: update 3"
output:
  html_notebook: default
  html_document: default
  pdf_document: default
---

```{r echo=F, message=F}
# source libraries and function
source('../required.R')

```

I've been doing a bit more digging on the data this week.  

Just to recap, the I've tested lots of the DSY files with lots of buildings. I've been looking at where the internal temperature $\Delta T > 0$  (because this affects all of the CIBSE overheating criteria). 

**However**, the times are the year where $\Delta T > 0$ are not the same for all buildings. I wanted to find out how this varied.

## How the buildings were set up

We used a simple building model and allowed some of the variables to change. These were: 

```{r}
var.file = '../data/all-variables-exp3.xlsx'
# file = 7 # choose the type of weather file
fold = 1 # folder 1 is DSY, folder 2 is TRY
days.spread = 3
variables=read.xlsx(var.file, sheetIndex = 1)
variables$Name = gsub('%%','', variables$Name)
kable(variables[variables$Vary.==1,c(2,3,4)])
```

Using these ranges, I selected 30 building using a Latin Hypercube method (next time I run the simulation, I'm going to use more samples...)

## Results so far

Each building was run using each of the 42 of the DSY files (3 weather files at each of the 14 locations). The hours where $\Delta T$ is greater than 0 were counted. 

Here's the output of a 30 building Newcastle DSY2 shown in both a stacked and histogram format: 

```{r}
source('../required.R')
save.folder = '../exp/exp3/'
# Analyse results - histrogram stacker ---------------------------------------------------------
results.f.names = paste(save.folder, dir(save.folder, pattern = '*.RDS'), sep='')
temp.data = make.plot.exp3(results.f.names, DSY.file.name = 'Newcastle_DSY2', n.build = no.buildings)
```

The results differ quite a bit for warmer locations like London, although there are commonalities across buildings: 

```{r}
temp.data = make.plot.exp3(results.f.names, DSY.file.name = 'London_DSY1', n.build = no.buildings)
```

## Delta T doesn't detect severity

As [Matt](mailto:m.e.eames@exeter.ac.uk) rightly pointed out today, $\Delta T$ doesn't affect severity. So next week I'll be working on ways to do that. If you have any good ideas, you [email me](mailto:michaelwoodguitar@gmail.com).
